Compiling refinement types to dependent types

### 2020-07-07 tex/paper.tex
Slightly better theorem wording

\begin{theorem}[Evaluation equivalence]
  For any well-typed surface language term $\nonterm{es}$, if $\nonterm{es}$ evaluates to v, then $\mu_\varepsilon(\nonterm{es})$ evaluates to $\mu_\varepsilon(v)$:
  %TODO symbols and all that for v
\end{theorem}
\begin{proof}
\end{proof}

>>>>

\begin{theorem}[Evaluation equivalence]
  If a well-typed surface language term $\nonterm{es}$ evaluates to v, then $\mu_\varepsilon(\nonterm{es})$ evaluates to $\mu_\varepsilon(v)$:
  %TODO symbols and all that for v
\end{theorem}
\begin{proof}
\end{proof}
